Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2025-12-22 revision_whittaker.tex
Cuts a few useless words
One more small cut

\begin{remarkplain} \textcolor{red}{[NEW]} {The group $Q$ is a finite abelian group, in fact an elementary abelian $2$-group. It is trivial when $G$ is adjoint, and when $G$ is simple  the cardinal of~$Q$ is at most~$4$. See Remark~\ref{rk:size_Q} for a more precise discussion.} \textcolor{red}{[/NEW]}\end{remarkplain}

@@

When $G(\R)$ is connected, which happens for instance if $G$ is simply connected, the group $G(\R)_{\ad}$ is itself connected, and therefore equal to the identity component of $\Gad(\R)$. In that case $Q_\sigma(\R)$ is isomorphic with the component group of $\Gad(\R)$.

>>>>

\begin{remarkplain} \textcolor{red}{[NEW]} {The group $Q$ is an elementary abelian $2$-group. It is trivial when $G$ is adjoint, and when $G$ is simple  the cardinal of~$Q$ is at most~$4$. See Remark~\ref{rk:size_Q} for a more precise discussion.} \textcolor{red}{[/NEW]}\end{remarkplain}

@@

When $G(\R)$ is connected, which happens for instance if $G$ is simply connected, the group $G(\R)_{\ad}$ is itself connected, and therefore equal to the identity component of $\Gad(\R)$. In that case $Q_\sigma(\R)$ is the component group of $\Gad(\R)$.
